---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snapcrackleprop

<!-- badges: start -->
<!-- badges: end -->

The goal of `snapcrackleprop` is to summarize the count and proportion of observations that meet one or more conditions within given group(s) of a data frame.

## Installation

You can install the latest version of `snapcrackleprop` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/snapcrackleprop")
```

The current version of `snapcrackleprop` is 0.1.0. 

## Dependencies

Note that `snapcrackleprop` version 0.1.0 depends on:   
- `dplyr`  
- `R version >= 4.1.0`  

## Example

This is a basic example using the `base R` data set `mtcars`. The following application of `group_count_and_prop` shows you how to summarize the count and proportion of observations where `mpg > 20` in each group by `cyl`. 

```{r example}
library(snapcrackleprop) 
group_count_and_prop(mtcars, # Input dataset
                     cyl, # Input variable(s) to group by
                     cond = mpg > 20) # Input condition(s) observations must meet 
```

