---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snapcrackleprop

<!-- badges: start -->
<!-- badges: end -->

The goal of `snapcrackleprop` is to summarize the count and proportion of observations that meet one or more conditions within given group(s) of a data frame.

## Installation

You can install the development version of `snapcrackleprop` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/snapcrackleprop", ref = "0.1.0")
```

## Example

This is a basic example using the `base R` data set `mtcars`. The following application of `group_count_and_prop` shows you how to summarize the count and proportion of observations where `mpg > 20` in each group by `cyl`. 

```{r example}
library(snapcrackleprop)
group_count_and_prop(mtcars, cyl, cond = mpg > 20)
```

